---
output: html_document
title: "Uniform Probability of Memory Sticks"
---


# Problem No.1:
A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

# Given
<b> <li> Memory sticks distributed uniformly between 2 and 12 mm </li>
</b>

<button onclick="hideoutput()" style="background: #e8ccd7;"> 
HIDE/SHOW
</button>
<div id="codeinputhere" style="display:block;">
```{r}
curve(dunif(x,2,12), 0, 14, xlab = "x", ylab = "Density", col = "blue")

x <- seq(0, 14, 0.001)

lines(x, dunif(x, 2,12), type = "h", col = "grey")

text(7, 0.1, "P(2 < X < 12)", col = "black", font = 2)

legend("topright", legend = c("PDF"), col = "blue")

```
</div>
<script>
function hideoutput() {
  var x = document.getElementById("codeinputhere");
  if (x.style.display === "block") {
    x.style.display = "none";
    
    
  } else {
    x.style.display = "block";
  }
}
</script>
# a.)Calculate the probability that a memory stick will be scrapped.

```{r letter_a, fig.html=TRUE}
1 - punif(10, 2,12)



```
<br>

<br>

# PDF / CDF

<b> <li> Probability density function & Cumulative Distribution Function </li>
</b>


<button onclick="hideoutput1()" style="background: #e8ccd7;"> 
HIDE/SHOW
</button>
<div id="codeinputhere1" style="display:block;">



```{r pdf_cdf, fig.html=TRUE}


par(mfrow = c(1, 2))

curve(dunif(x, 10, 12), xlim = c(2, 12), ylab="", main = "PDF",xlab="Length (mm)")

curve(punif(x, 10, 12), xlim = c(2, 12), ylab="",main = "CDF",xlab="Length (mm)")
```
</div>
<script>
function hideoutput1() {
  var x = document.getElementById("codeinputhere1");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>





# b.) Histogram of Memory Stick (without scrapped)
```{r letter_a2, fig.html=TRUE}
set.seed(123)
x <- runif(50, 2, 12)
x <- x[x <= 10]
hist(x, main = "Histogram of Memory Stick ", xlab = "Length (mm)", col="pink")

sim_mean <- mean(x)
sim_var <- var(x)

cat("Simulated Mean:", sim_mean, "\n")
cat("Simulated Variance:", sim_var)
```


<br>
<br>
<br>

# Problem No.2:
Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf

$$ f(x) = 0.025x + b,  2<x<6 $$


# PDF / CDF

<b> <li> Probability density function & Cumulative Distribution Function </li>
</b>


<button onclick="hideoutput2()" style="background: #e8ccd7;"> 
HIDE/SHOW
</button>
<div id="codeinputhere2" style="display:block;">




```{r pdfcdf no2, fig.html=TRUE}
par(mfrow = c(1, 2))
curve(dunif(x, 2, 6), xlim = c(0, 8), ylab="", main = "PDF")


curve(punif(x, 2, 6), xlim = c(0, 8), ylab="",main = "CDF")

```

</div>
<script>
function hideoutput2() {
  var x = document.getElementById("codeinputhere2");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>





# a.) Let <b> b=0.15 </b> as desired. <br>
Getting the Probability Density Function of X
    

```{r a no2, fig.html=TRUE}

b <- 0.15

funct <- function(x) {
  0.025*x + b
}

curve(funct, 2, 6, xlim = c(0, 8))

integral <- integrate(funct, 2, 6)
answer <- integral[["value"]]

cat("The Integral is equals to", answer, "\n")




```

Since According to the 1st Property of <i> pdf </i> of X which is; <br> 

$$\int_{-\infty}^{\infty} f(x) dx = 1$$

<br> <b> $\therefore\ b \text{ is indeed equal to } 0.15$
 </b>
 <br> <br> 
 
# b.) Find the probability that the measurement of the current exceeds 3.
 

```{r b no2, fig.html=TRUE}

a <- 3

exceed3 <- integrate(funct, a,  6)
answer_2 <- exceed3[["value"]]
cat("The probability that the measurement exceeds 3 is", round(answer_2, 3))
```

<br> <b> $\therefore\ \text{ The probability that the measurement exceeds 3 is 0.7875  }$
 </b><br> <br> 

# c.)  Find E(X).
 

```{r c no2, fig.html=TRUE}

b <- 0.15

funct <- function(x) {
  0.025*x + b
}
newinteg <- function(x) {x * funct(x)}

e_x <- integrate(newinteg, 2, 6)

answer_3 <- e_x [["value"]]
# Print the result
cat("E(X) is", round(answer_3, 2))


```

<br> <b> $\therefore\ \text{ E(X) is 4.13  }$
 </b>


<br>
<br>
<br>

# Problem No.3:
$$ \text {In a radio communications system, the phase difference X between  the transmitter} $$
$$ \text { and receiver is modeled as having a uniform density in [−𝜋,+𝜋]. Find
P(X ≤ 0) and P(X ≤ 𝜋∕2).}$$


<br>
<br>

# PDF / CDF

<b> <li> Probability density function & Cumulative Distribution Function </li>
</b>


<button onclick="hideoutput3()" style="background: #e8ccd7;"> 
HIDE/SHOW
</button>
<div id="codeinputhere3" style="display:block;">


```{r figure3, fig.html=TRUE}


par(mfrow = c(1, 2))
curve(dunif(x, -pi, pi), xlim = c(-10, 10), ylab="", main = "PDF")
curve(punif(x, -pi, pi), xlim = c(-10, 10), ylab="", main = "CDF")


```

</div>
<script>
function hideoutput3() {
  var x = document.getElementById("codeinputhere3");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>




<br>
Using the Definition of PDF 

$$
f(x) = \begin{cases}
      \frac{1}{b-a}, & \text{if}\ a \leq x \leq b \\
      0, & \text{otherwise}
    \end{cases}
$$

Let a= 𝜋 and b =𝜋

```{r no3, fig.html=TRUE}

a <- -pi
b <- pi


PDF <- Vectorize(function(x) {
  if (x < a || x > b) {
    return(0)
  }
  return(1 / (b - a))
})

p_0 <- integrate(PDF, a, 0)
answer_4 <- p_0 [["value"]]

p_over_2 <- integrate(PDF, a, pi/2)
answer_5 <- p_over_2 [["value"]]

cat("P(X ≤ 0) =", answer_4, "\n")
cat("P(X ≤ 𝜋/2) =", answer_5, "\n")


```


<br> <b> $\therefore\ \text{ P(X ≤ 0) is 0.5  }$
 </b>
 
 <br> <b> $\therefore\ \text{ P(X ≤ 𝜋/2) is 0.75  }$
 </b>
